\chapter{Definition of soft matter}
Soft matter is plastic (polymers), water (liquids), air (gas), liquid crystals
and colloidal suspensions (particles in liquid), gels, sand (granural
materials). Also active matter (such as bacteria and fishes and birds are soft
matters in some sense).\\

What is not soft matter: graphite is a dense matter, but grapheene is a soft
matter. metals functionalized with proteions or nanoparticles could be
considered as soft matter. \\

Poor definition: % To add definitions, remember to put in the prefix
% the command \newtheorem{definition}{Definition}
\begin{definition}
    Soft matter systems SM systems are deformable
    upon stresses
    of the order of magnitude
    of thermal fluctuations
    
\end{definition} 
This is an antropocentric definition! as in fact you are referring to our body
termperature. Some elements become soft matter with the Temperature. \\

Soft matter is \textbf{mesoscopic}: RELEVANT STRUCTURES
ARE MUCH LARGER
THAN THE CONSTITUENTS
BUT MUCH SMALLER
THAN THE WHOLE --> you don't need very profound analysis to define and
characterize your system.
By coarse graining, you have to select space and time scales that are good for
your system. \\

\begin{center}
    \textbf{
        In general, you generate a coarse-grained system whenever you consider as
        indipendent compounds groups of atoms. The larger the size of the
        phenomena you are trying to observe, the less are the important details
        you have to consider!
        }    
\end{center}

The first level of approximation is done through the Born-Oppneheimer
approximation, in fact through that method you can consider the electrons and
the nuclei separately (at first by solving the so called the electronic problem,
after by solving the motion of nuclei through Newton mechanics).

To go from a scale to another, you need a mapping function $\vec{R}_I = M(\vec{r})$. This determines
\begin{itemize}
  \item loss of degrees of freedom (loss of information). in fact, several high
  resolution can produce the same low resolution arrangement.
  \item substantial increase of entropy in the system: you gain an effective
  entropy that you have to take into account, although you loose some
  simplifying.
\end{itemize}

Machine L. can be used to extract features useful for the coarse graining.